A game theoretic model of the behavioural gaming that takes place at the EMS - ED interface\tnoteref{t1}

### 2022-03-29 sections/model_overview/numerical_results/main.tex
Scale payoff matrices to be more presentable

Matrices \(A\) and \(B\) represent the original payoff matrices while matrices
\(\tilde{A}\) and \(\tilde{B}\) represent the incentivised payoff matrices.
It can be observed that matrix \(\tilde{A}\) is a scaled version of matrix 
\(A\) only on the row that is most frequently played and similarly matrix 
\(\tilde{B}\) of matrix \(B\) only on the column that is most frequently played
(matrix \(A\): row \(5\), matrix \(B\): column \(6\), see Figure 
\ref{fig:ard_penalty}).
Note that the values of the payoff matrices only differ on the fourth digit
which is the raw utility of the strategies played.

\tiny
\begin{equation*}
    A = 
    \begin{bmatrix}
        0.9995052 & 0.9995052 & 0.9995052 & 0.9995052 & 0.9995052 
        & 0.9995052 & 0.9995052 \\
        0.99954989 & 0.99954978 & 0.99954961 & 0.99954924 & 0.99954845 
        & 0.9995466 & 0.999539 \\
        0.99968233 & 0.99968194 & 0.99968151 & 0.99968067 & 0.99967874 
        & 0.9996734 & 0.999649  \\
        0.99990299 & 0.99990245 & 0.99990189 & 0.99990081 & 0.99989832
        & 0.9998909 & 0.9998517 \\
        \color{blue}0.99999996 & \color{blue}0.99999994 & \color{blue}0.99999992 
        & \color{blue}0.99999988 & \color{blue}0.99999973 & \color{blue}0.9999989 
        & \color{blue}0.9999859 \\
        0.9998773 & 0.99987995 & 0.99988236 & 0.99988643 & 0.99989417 
        & 0.9999126 & 0.9999712
    \end{bmatrix}
\end{equation*}

\begin{equation*}
    B = 
    \begin{bmatrix}
        0.99917127 & 0.99925823 & 0.99946188 & 0.99968499 & 0.9998942 
        & \color{red}1.0 & 0.99982128 \\
        0.99917127 & 0.99925479 & 0.99945638 & 0.99968051 & 0.99989153 
        & \color{red}0.99999997 & 0.9998333  \\
        0.99917127 & 0.99924532 & 0.99943793 & 0.99966451 & 0.99988286 
        & \color{red}0.99999966 & 0.99985269 \\
        0.99917127 & 0.99924146 & 0.99942878 & 0.99965484 & 0.99987667 
        & \color{red}0.99999921 & 0.99986701 \\
        0.99917127 & 0.9992342 &  0.99941013 & 0.99963286 & 0.99986077 
        & \color{red}0.9999972 & 0.9998958  \\
        0.99917127 & 0.99921279 & 0.99934961 & 0.99954933 & 0.99978407 
        & \color{red}0.99997106 & 0.99997276 \\
    \end{bmatrix}
\end{equation*}

\begin{equation*}
    \tilde{A} = 
    \begin{bmatrix}
        0.99950518 & 0.99950518 & 0.99950518 & 0.99950518 & 0.99950518
        & 0.99950518 & 0.99950518 \\
        0.99954989 & 0.99954978 & 0.99954961 & 0.99954924 & 0.99954845
        & 0.99954656 & 0.99953879 \\
        0.99968233 & 0.99968194 & 0.99968151 & 0.99968067 & 0.99967874
        & 0.99967339 & 0.9996492  \\
        0.99990299 & 0.99990245 & 0.99990189 & 0.99990081 & 0.99989832
        & 0.9998909 & 0.99985171 \\
        \color{blue}0.99969996 & \color{blue}0.99969994 & \color{blue}0.99969992 
        & \color{blue}0.99969988 & \color{blue}0.99969973 & \color{blue}0.99969895 
        & \color{blue}0.99968586 \\
        0.9998773 &  0.99987995 & 0.99988236 & 0.99988643 & 0.99989417
        & 0.99991264 & 0.99997122 \\
    \end{bmatrix}
\end{equation*}

\begin{equation*}
    \tilde{B} = 
    \begin{bmatrix}
        0.99917127 & 0.99925823 & 0.99946188 & 0.99968499 & 0.9998942
        & \color{red}0.9997 & 0.99982128 \\
        0.99917127 & 0.99925479 & 0.99945638 & 0.99968051 & 0.99989153
        & \color{red}0.99969997 & 0.9998333 \\
        0.99917127 & 0.99924532 & 0.99943793 & 0.99966451 & 0.99988286
        & \color{red}0.99969966 & 0.99985269 \\
        0.99917127 & 0.99924146 & 0.99942878 & 0.99965484 & 0.99987667
        & \color{red}0.99969921 & 0.99986701 \\
        0.99917127 & 0.9992342 &  0.99941013 & 0.99963286 & 0.99986077
        & \color{red}0.9996972 & 0.9998958 \\
        0.99917127 & 0.99921279 & 0.99934961 & 0.99954933 & 0.99978407
        & \color{red}0.99967106 & 0.99997276 \\
    \end{bmatrix}
\end{equation*}
\normalsize

>>>>

Matrices \(A\) and \(B\) represent the original payoff matrices while matrices
\(\tilde{A}\) and \(\tilde{B}\) represent the incentivised payoff matrices.
It can be observed that matrix \(\tilde{A}\) is a scaled version of matrix 
\(A\) only on the row that is most frequently played and similarly matrix 
\(\tilde{B}\) of matrix \(B\) only on the column that is most frequently played
(matrix \(A\): row \(5\), matrix \(B\): column \(6\), see Figure 
\ref{fig:ard_penalty}).
Note that for the presentation of data, a scaling has been applied to obtain
the values of the payoff matrices.
The results are not affected by this scaling.

\tiny
\begin{equation*}
    A = 
    \begin{bmatrix}
        5.0518 & 5.0518 & 5.0518 & 5.0518 & 5.0518 &
        5.0518 & 5.0518 \\
        5.4989 & 5.4977 & 5.4960 & 5.4924 & 5.4844 &
        5.4654 & 5.3875 \\
        6.8232  & 6.8192 & 6.8150 & 6.8065 & 6.7871  &
        6.7334 & 6.4906 \\
        9.0298 & 9.0244 & 9.0187 & 9.0078 & 8.9827 &
        8.9082 & 8.5145 \\
        \color{blue}9.9996 & \color{blue}9.9994 & \color{blue}9.9992 & 
        \color{blue}9.9987 & \color{blue}9.9972 & \color{blue}9.9893 & 
        \color{blue}9.8571 \\
        8.7740 & 8.8006 & 8.8249 & 8.8660 & 8.9438 &
        9.1295 & 9.7157
    \end{bmatrix}
\end{equation*}

\begin{equation*}
    B = 
    \begin{bmatrix}
        1.7127 & 2.5822 & 4.6186 & 6.8497 & 8.9418 &
        \color{red}9.9999 & 8.2148 \\
        1.7127 & 2.5477 & 4.5634 & 6.8047 & 8.9150  &
        \color{red}9.9996 & 8.3358 \\
        1.7127 & 2.4528    & 4.3784 & 6.6441 & 8.8278 &
        \color{red}9.9965 & 8.5306 \\
        1.7127 & 2.4141 & 4.2867 & 6.5470 & 8.7656 &
        \color{red}9.9919 & 8.6745 \\
        1.7127 & 2.3415 & 4.0998 & 6.3265 & 8.6058 &
        \color{red}9.9716 & 8.9634 \\
        1.7127 & 2.1269 & 3.4930 & 5.4885 & 7.8353 &
        \color{red}9.7075 & 9.7322 \\
    \end{bmatrix}
\end{equation*}

\begin{equation*}
    \tilde{A} = 
    \begin{bmatrix}
        5.0518 & 5.0518 & 5.0518 & 5.0518 & 5.0518 &
        5.0518 & 5.0518  \\
        5.4989 & 5.4977 & 5.4960 & 5.4924 & 5.4844 &
        5.4654 & 5.3875 \\
        6.8232 & 6.8192 & 6.8150 & 6.8065 & 6.7871 &
        6.7334 & 6.4906 \\
        9.0298 & 9.0244 & 9.0187 & 9.0078 & 8.9827 &
        8.9082 & 8.5145 \\
        \color{blue}6.9996 & \color{blue}6.9994 & \color{blue}6.9992 & \color{blue}6.9987  & \color{blue}6.9972 &
        \color{blue}6.9893 & \color{blue}6.8571 \\
        8.7740 & 8.8006 & 8.8249 & 8.8660 & 8.9438 &
        9.1295 & 9.7157 \\
    \end{bmatrix}
\end{equation*}

\begin{equation*}
    \tilde{B} = 
    \begin{bmatrix}
        1.7127 & 2.5822 & 4.6186 & 6.8497 & 8.9418 &
        \color{red}6.9999 & 8.2148 \\
        1.7127 & 2.5477 & 4.5634 & 6.8047 & 8.9150 &
        \color{red}6.9996 & 8.3358 \\
        1.7127 & 2.4528   & 4.3784 & 6.6441 & 8.8278 &
        \color{red}6.9965 & 8.5306 \\
        1.7127 & 2.4141 & 4.2867 & 6.5470 & 8.7656 &
        \color{red}6.9919 & 8.6745 \\
        1.7127 & 2.3415 & 4.0998 & 6.3265 & 8.6058 &
        \color{red}6.9716 & 8.9634  \\
        1.7127 & 2.1269 & 3.4930 & 5.4885 & 7.8353 &
        \color{red}6.7076 & 9.7322 \\
    \end{bmatrix}
\end{equation*}
\normalsize
